Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Updated Figure 12

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs, 
      aes(x = sqrt_row_wise_total_error, 
          y = density,
          colour = factor(error_cat_n, levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("b1",
                      position = c(0.95, 0.9),
                      cex = 1.5) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs,
        aes(x = sqrt_row_wise_total_error, 
            y = density,
            colour = factor(error_cat_n2, levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("a1",
                      position = c(0.95, 0.9),
                      cex = 1.5) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))
```

```{r}
#| label: link-model-one-dens-clust
plot_tsne_dens <- error_df_one_curvy_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = factor(error_cat_n2,
                             levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  theme(aspect.ratio = 1) +
  interior_annotation("a2",
                      position = c(0.08, 0.9),
                      cex = 1.5)

plot_tsne_dens_selected <- error_df_one_curvy_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = factor(error_cat_n,
                             levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  theme(aspect.ratio = 1) +
  interior_annotation("b2",
                      position = c(0.08, 0.9),
                      cex = 1.5)

@@

five_c_shaped_proj_tsne_model1 <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 1.5,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")

@@

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 1.5,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")
```

>>>>

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs, 
      aes(x = sqrt_row_wise_total_error, 
          y = density,
          colour = factor(error_cat_n, levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("b1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs,
        aes(x = sqrt_row_wise_total_error, 
            y = density,
            colour = factor(error_cat_n2, levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("a1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))
```

```{r}
#| label: link-model-one-dens-clust
plot_tsne_dens <- error_df_one_curvy_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = factor(error_cat_n2,
                             levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  theme(aspect.ratio = 1) +
  interior_annotation("a2",
                      position = c(0.08, 0.9),
                      cex = 2)

plot_tsne_dens_selected <- error_df_one_curvy_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = factor(error_cat_n,
                             levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  theme(aspect.ratio = 1) +
  interior_annotation("b2",
                      position = c(0.08, 0.9),
                      cex = 2)

@@

five_c_shaped_proj_tsne_model1 <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")

@@

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")
```
